hbm_paper_results

### 2024-02-15 paper_main_results.Rmd
adding code to ID larger group level

mean.cent.diffs.long %>%
  dplyr::filter(dataset != "ukb_CN") %>%
  ggplot() +
  geom_histogram(aes(x=cent_abs.diff, fill=dataset, y = stat(width*density)), color="black", alpha=0.6, position="identity") +
  theme_linedraw(base_size = 11) +
  facet_grid(dataset~pheno_cat) +
  scale_y_continuous(labels = scales::percent) + 
  labs(y="Percent Features", x = "Mean Absolute Centile Error") +
  ggtitle("Absolute errors in centiles of brain structure features across ComBat processing pipelines")
```

@@

@@

<!-- ### W/o extremes -->
Are extreme z-scores (<-2 and >2) driving observed results?

>>>>

mean.cent.diffs.long %>%
  dplyr::filter(dataset != "ukb_CN") %>%
  ggplot() +
  geom_histogram(aes(x=cent_abs.diff, fill=dataset, y = stat(width*density)), color="black", alpha=0.6, position="identity") +
  theme_linedraw(base_size = 11) +
  facet_grid(dataset~pheno_cat) +
  scale_y_continuous(labels = scales::percent) + 
  labs(y="Percent Features", x = "Mean Absolute Centile Error") +
  ggtitle("Absolute errors in centiles of brain structure features across ComBat processing pipelines")
```
Quick comp of cf.gam and cf.gamlss

```{r}
gam.gamlss.diffs <- diffs.df %>%
  dplyr::filter(dataset=="cf.gam" | dataset=="cf.gamlss")

gam_better <- gam.gamlss.diffs %>%
  group_by(dataset) %>%
  summarize_at(pheno_abs.diff.list, median) %>%
  ungroup() %>%
  pivot_longer(cols = all_of(pheno_abs.diff.list), names_to="pheno") %>%
  pivot_wider(names_from = dataset, values_from=value, names_glue = "med_{dataset}") %>%
  mutate(gam_minus_gamlss = (med_cf.gam - med_cf.gamlss),
         pheno = sub("abs.diff_", "", pheno)) %>%
  ungroup() %>%
  dplyr::filter(gam_minus_gamlss < 0)

gam_better$pheno

ns_gam_gamlss_comp <- full_cent_res %>%
  dplyr::filter(comp=="cf.gamlss_cf.gam" & sig_fdr == TRUE)

intersect(gam_better$pheno, ns_gam_gamlss_comp$pheno)
```
```{r, eval=FALSE}
for (pheno in pheno_abs.diff.list){
  p <- ggplot(gam.gamlss.diffs, aes(y = gam.gamlss.diffs[[pheno]], fill= dataset)) +
      geom_boxplot() +
    ggtitle(pheno)
print(p)
}
```

**21 regions where ComBat GAM is better than ComBat-LS! All cortical thickness -> 206-21 = 185 regions where ComBat-LS fits better.

@@

Quick comp of cf.gam and cf.gamlss

```{r, message=FALSE}
full_z_res <- centile.t.tests.full_result(diffs.df, feature_list=z.pheno_abs.diff.list)
```

```{r}
gam_better.z <- gam.gamlss.diffs %>%
  group_by(dataset) %>%
  summarize_at(z.pheno_abs.diff.list, median) %>%
  ungroup() %>%
  pivot_longer(cols = all_of(z.pheno_abs.diff.list), names_to="pheno") %>%
  pivot_wider(names_from = dataset, values_from=value, names_glue = "med_{dataset}") %>%
  mutate(gam_minus_gamlss = (med_cf.gam - med_cf.gamlss),
         pheno = sub("abs.diff_", "", pheno)) %>%
  ungroup() %>%
  dplyr::filter(gam_minus_gamlss < 0)

gam_better.z$pheno

ns_gam_gamlss_comp.z <- full_z_res %>%
  dplyr::filter(comp=="cf.gamlss_cf.gam" & sig_fdr == TRUE)

intersect(gam_better.z$pheno, ns_gam_gamlss_comp.z$pheno)
```

@@

### W/o extremes
Are extreme z-scores (<-2 and >2) driving observed results?
